---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 5"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 5.  Availability Heuristic and Individual Motivation (T1)

- Null: Availability of positive or negative examples will not affect individual motivation to innovate (T1).

```{r}
cat(readLines("bayesGlmer_h5_h5.0_summary.txt"), sep = '\n')
```
- Prediction 1: Availability of a positive example will increase individual motivation to innovate (T1), while availability of a negative example will decrease individual motivation to innovate (T1).
```{r}
cat(readLines("bayesGlmer_h5_h5.1_summary.txt"), sep = '\n')
```
- Prediction 2: Availability of a negative example will decrease individual motivation to innovate (T1).
```{r}
cat(readLines("bayesGlmer_h5_h5.2_summary.txt"), sep = '\n')
```

```{r h5BFs}
source("functions.R")
Bf_plotter("BFs5.csv")
```
End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
