---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 18"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 18. Conformity and Individual Motivation to Innovate (T2)

- Null: Group Conformity will not moderate Individual Motivation to Innovate (T2).

```{r comment=''}
cat(readLines("bayesGlmer_h18_h18.0_summary.txt"), sep = '\n')
```
- Prediction 1: Group Conformity will moderate Individual Motivation to Innovate (T2). When group motivation to innovate is positive, conformity increases Individual Motivation to Innovate (T2). When group motivation to innovate is negative, conformity decreases Individual Motivation to Innovate (T2).

```{r, fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs18.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
