---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 4"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 4. Tolerance of Ambiguity and Innovation Uncertainty

- Null: TA will not moderate the effect of Innovation Uncertainty on Innovative Prospect Value. Individuals high in TA will show the same certainty effect than individuals low in TA. 

```{r}
cat(readLines("bayesGlmer_h4_h4.0_summary.txt"), sep = '\n')
```
- Prediction 1: TA will moderate the effect of Innovation Uncertainty on Innovative Prospect Value. Individuals high in TA will show a lower certainty effect than individuals low in TA.

```{r, fig.hold='hold', fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs4.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
