---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 7"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list = ls(all = TRUE))
dd <- getwd()
od <- getwd()
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, strip.white=TRUE, tidy=TRUE)
# load libraries
library("RCurl")
library("bridgesampling")
library("rstanarm")

# Setup Stan parameters

options(mc.cores = parallel::detectCores())
nChains <- 3
nIter <- 50000

# download scripts and data
dlScripts <- function (scriptNames) {
  fileHolder <- getURL(paste(githubRepo, scriptNames, sep = "/"), ssl.verifypeer = FALSE)
  fileConn<-file(scriptNames)
  writeLines(fileHolder, fileConn)
  close(fileConn)
}
githubRepo <- "https://raw.githubusercontent.com/GallupGovt/ngs2/master/cycle4/Boomtown/Analysis"
setup <- c("functions.R", "prep.R")
hypotheses <- c("h7.R")
data <- c("game_data.csv", "game_data_group.csv")
lapply(c(setup, hypotheses, data), dlScripts)

# Prepare data
source("functions.R")
source("prep.R")
source ("h7.R")
summarize_delete ("bayesGlmer_h7_h7.0")
summarize_delete ("bayesGlmer_h7_h7.1")
summarize_delete ("bayesGlmer_h7_h7.2")
print ("h7.R complete!")
```
### Hypothesis 7. Perceived Intergroup Competition and Heuristic Reasoning

- Null: Perceived intergroup competition does not moderate the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have the same effect on individuals facing strong competition as those facing balanced or weak competition.

```{r comment=''}
cat(readLines("bayesGlmer_h7_h7.0_summary.txt"), sep = '\n')
```
- Prediction 1: Perceived intergroup competition moderates the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have a greater effect on individuals facing strong competition than those facing balanced or weak competition. 
- Prediction 2: Perceived intergroup competition moderates the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have a smaller effect on individuals facing strong competition than those facing balanced or weak competition.

```{r, fig.hold='hold', out.width = "50%"}
Bf_plotter("BFs7.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />