---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 11"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 11. Complexity of Innovation and Heuristic Reasoning

- Null: Innovation complexity does not moderate the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will not have a greater effect on individual motivation to innovate under high complexity than under low complexity.

```{r comment=''}
cat(readLines("bayesGlmer_h11_h11.0_summary.txt"), sep = '\n')
```
- Prediction 1: Innovation complexity moderates the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have a greater effect on individual motivation to innovate under high complexity than under low complexity.

```{r, fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs11.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
