---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 1"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 1. Intergroup Competition and Individual Motivation to Innovate (T1)

- Null: Intergroup competition has no effect on individual motivation to innovate (T1).

```{r comment=''}
cat(readLines("bayesGlmer_h1_h1.0_summary.txt"), sep = '\n')
```

- Prediction 1: Intergroup competition increases Individual Motivation to Innovate (T1).
- Prediction 2: Individual Motivation to Innovate (T1) is u-shaped on intergroup competition.
- Prediction 3: Low intergroup competition decreases Individual Motivation to Innovate (T1).

```{r, fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs1.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
