---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 7"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list = ls(all = TRUE))
dd <- getwd()
od <- getwd()
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, strip.white=TRUE, tidy=TRUE)
# load libraries
if (!require("pacman")) install.packages("pacman", repos='http://cran.us.r-project.org')
library ("pacman")
pacman::p_load(rstan, rstanarm, ggplot2, Hmisc, httr, bridgesampling, DT, dplyr, bayesplot, knitr, lme4, RCurl, formatR, caret, pROC, formatR, foreach, doParallel, forcats, tidyr, car)

# Setup Stan parameters

options(mc.cores = parallel::detectCores())
nChains <- 3
nIter <- 50000

# download scripts and data
dlScripts <- function (scriptNames) {
  fileHolder <- getURL(paste(githubRepo, scriptNames, sep = "/"), ssl.verifypeer = FALSE)
  fileConn<-file(scriptNames)
  writeLines(fileHolder, fileConn)
  close(fileConn)
}
githubRepo <- "https://raw.githubusercontent.com/GallupGovt/ngs2/master/cycle3/Boomtown/Analysis"
setup <- c("functions.R", "prep.R")
hypotheses <- c("h7.R")
data <- c("game_data.csv", "game_data_group.csv")
lapply(c(setup, hypotheses, data), dlScripts)

# Prepare data
source("functions.R")
source("prep.R")
source ("h7.R")
summarize_delete ("bayesGlmer_h7_h7.0")
summarize_delete ("bayesGlmer_h7_h7.1")
summarize_delete ("bayesGlmer_h7_h7.2")
print ("h7.R complete!")
```
### Hypothesis 7. Perceived Intergroup Competition and Heuristic Reasoning

- Null: Perceived intergroup competition does not moderate the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have the same effect on individuals facing strong competition as those facing balanced or weak competition.

```{r h7null}
load (file ="bayesGlmer_h7_h7.0")
fittedGlmer
```
- Prediction 1: Perceived intergroup competition moderates the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have a greater effect on individuals facing strong competition than those facing balanced or weak competition. 

```{r }
load (file ="bayesGlmer_h7_h7.1")
fittedGlmer
```

- Prediction 2: Perceived intergroup competition moderates the effect of heuristic reasoning on individual motivation to innovate (T1): The availability heuristic will have a smaller effect on individuals facing strong competition than those facing balanced or weak competition.

```{r }
load (file ="bayesGlmer_h7_h7.2")
fittedGlmer
```

```{r h7BFs}
BFs7 <-read.csv(paste(od, "BFs7.csv", sep = '/'))                      
BFs7
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />