---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 6"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 6. Exogenous Uncertainty and Individual Motivation (T1)

- Null: Increased exogenous uncertainty (ignorance) will not affect individual motivation to innovate (T1)
- Prediction 1: Increased exogenous uncertainty (ignorance) will increase individual motivation to innovate (T1).
```{r}
cat(readLines("bayesGlmer_h6.1_h6.1null_summary.txt"), sep = '\n')
```
- Prediction 2: Exogenous uncertainty (ignorance) will decrease individual motivation to innovate (T1) in the early stages of the game.
```{r}
cat(readLines("bayesGlmer_h6.2_h6.2null_summary.txt"), sep = '\n')
```
```{r, fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs6.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
