---
title: "Group Innovation under Competition and Uncertanity - Cycle 4 Fieldwork Report"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: no
    theme: united
    toc: no
  pdf_document:
    toc: no
  word_document:
    toc: no
---

# Data Processing

```{r setup, include=FALSE}
rm(list = ls(all = TRUE))
dd <- getwd()
od <- getwd()
# load libraries
if (!require("pacman")) install.packages("pacman")
library ("pacman")
pacman::p_load(ggplot2, httr, dplyr, knitr, RCurl, formatR, DT)
# download scripts and data
dlScripts <- function (scriptNames) {
  fileHolder <- getURL(paste(githubRepo, scriptNames, sep = "/"), ssl.verifypeer = FALSE)
  fileConn<-file(scriptNames)
  writeLines(fileHolder, fileConn)
  close(fileConn)
}
githubRepo <- "https://raw.githubusercontent.com/GallupGovt/ngs2/master/cycle4/Boomtown/Analysis"
setup <- c("wrangle.R", "analytics.R")
data <- c("game_data.csv", "survey_data.csv") # Run "wrangle.R" first and upload these resulting files to Github
lapply(c(setup, data), dlScripts)
```

- Boomtown data processed successfully!
- There are no duplicate values of 'playerid'
- The values of survey items are in their correct range

# Data Summary

```{r analytics, include=FALSE}
#Load data processed by "wrangle.r" and run analytics
factorial <- read.csv(file="game_data.csv")
survey <- read.csv(file="survey_data.csv")
source("analytics.R")
```

* Valid experimental instances included games with at least seven players and one tool choice. 
* Each round of data collection included:
    + 96 experimental conditions in the full factorial space.
    + 672 players (7 players per instance)
    + 1,248 group choices (13 rounds per instance)
    + 8,736 individual choices (7 players * 13 rounds per instance)
* Since Cycle 4 experiments were launched, Gallup has: 
    + Ran a total of `r nGames` valid instances.
    + Obtained usable data from a total of `r nPlayers` players.
    + Completed data collection for `r nConditions` of the 96 experimental conditions in the full factorial space.

```{r settingCounts}
print(setting_counts)
```

# Games completed to date

```{r samplePlots}
dates$month <- format(dates$matchDate, "%m/%Y")
dates %>% group_by(month) %>% summarise(games = n())
barplot(table(dates$matchDate))
table(dates$matchDate)
print (hourly_plot)
```

# Data sample

Variables used and a random sample of rows from the final analytical dataset are summarized below. 

```{r data header}
names(factorial)
datatable(sample_n(factorial, 5), 
          caption = "Randomly selected rows of processed data.",
          options = list(
              scrollX = TRUE,
              scrollCollapse = TRUE))
```
