---
title: "Group Innovation under Competition and Uncertanity - Cycle 4 Fieldwork Report"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: no
    theme: united
    toc: no
  pdf_document:
    toc: no
  word_document:
    toc: no
---

# Data Processing

```{r setup, include=FALSE}
rm(list = ls(all = TRUE))
dd <- getwd()
od <- getwd()
# load libraries
if (!require("pacman")) install.packages("pacman")
library ("pacman")
pacman::p_load(ggplot2, httr, dplyr, knitr, RCurl, formatR, DT, car, tidyr)
# download scripts and data
dlScripts <- function (scriptNames) {
  fileHolder <- getURL(paste(githubRepo, scriptNames, sep = "/"), ssl.verifypeer = FALSE)
  fileConn<-file(scriptNames)
  writeLines(fileHolder, fileConn)
  close(fileConn)
}
githubRepo <- "https://raw.githubusercontent.com/GallupGovt/ngs2/master/cycle4/Boomtown/Analysis"
setup <- c("wrangle.R", "analytics.R", "survey_tests_cycle_4_code.R")
data <- c("game_data.csv", "game_survey_data.csv", "tool_checks.csv") # Run "wrangle.R" first and upload these resulting files to Github
lapply(c(setup, data), dlScripts)
```

- Boomtown data processed successfully!
- There are no duplicate values of 'playerid'
- The values of survey items are in their correct range

# Data Summary

```{r analytics, include=FALSE}
#Load data processed by "wrangle.r" and run analytics
factorial <- read.csv(file="game_data.csv")
game_survey_data <- read.csv(file="game_survey_data.csv")
tool_checks <- read.csv(file="tool_checks.csv", stringsAsFactors = F)
source("analytics.R")
source("survey_tests_cycle_4_code.R")
```

* Valid experimental instances included games with at least seven players and one tool choice. 
* Each round of data collection included:
    + 96 experimental conditions in the full factorial space.
    + 672 players (7 players per instance)
    + 1,248 group choices (13 rounds per instance)
    + 8,736 individual choices (7 players * 13 rounds per instance)
* Since Cycle 4 experiments were launched, Gallup has: 
    + Ran a total of `r nGames` valid instances.
    + Obtained usable data from a total of `r nPlayers` players.
    + Completed data collection for `r nConditions` of the 96 experimental conditions in the full factorial space.

```{r settingCounts}
print(setting_counts)
```

# Experiments completed to date

```{r datePlots, echo=FALSE, fig.height = 5, fig.width = 10}
dates$month <- format(dates$matchDate, "%m/%Y")
dates %>% group_by(month) %>% summarise(games = n())
barplot(table(dates$matchDate), 
        main="Number of successful experiments by date",
        ylab="Number of experiments", las = 3, cex.names=0.75)
```

```{r datetable, echo=FALSE}
table(dates$matchDate)
```

```{r hourlyPlots, echo=FALSE, fig.height = 25, fig.width = 7}
hourly_plot
```

# Participant Demos

```{r demos, echo=FALSE}
initial_survey <- gs[!duplicated(gs[,c('playerid')]),] 
demos <- c("Age_Group", "Gender", "Education_Group", "Employment_Status", "Online_Research_Experience")
apply(initial_survey[demos], 2, table, useNA = "always")
```
# Descriptives
```{r descriptives, echo=FALSE}
# Number of rounds
nByround=factorial%>%
  group_by(round=as.factor(round))%>%
  summarise(counts  = n())
nChoices<-sum(nByround$counts)
nMax<- max(nByround$counts)
ggplot(data=nByround, aes(x=round, y=counts)) +
  geom_bar(stat="identity") +
  ggtitle("Number of Choices") + 
  xlab("Round") +
  ylab("Total Choices by Round")+
  annotate("text", x=7, y=nMax*1.15, label = paste("Total to date =", nChoices, "valid decisions in 13 rounds")) +
  scale_y_continuous(limits = c(0, nMax*1.25))
# By tool choice
factorial.tools<-subset(factorial, tools!="9" & tools!="10" & tools!="11" & tools!="12")
factorial.tools$innovation2<- as.numeric(factorial.tools$innovation)
tool_rate1<-factorial.tools%>%
  group_by(tools)%>%
  summarise(rate_inn=mean(innovation2, na.rm=TRUE))
ggplot(data=tool_rate1, aes(x=tools, y=rate_inn)) +
  geom_bar(stat="identity") +
  ggtitle("Innovative Choices by Tool Choice") + 
  xlab("Tool Choice") +
  ylab("Innovative Choice Rate")
```

# Data sample

Variables used and a random sample of rows from the final analytical dataset are summarized below. 

```{r data header, echo=FALSE}
names(factorial)
datatable(sample_n(factorial, 5), 
          caption = "Randomly selected rows of processed data.",
          options = list(
              scrollX = TRUE,
              scrollCollapse = TRUE))
```
