---
title: |
  | NGS2 Cycle 4 Survey Test Results
author: "Ying Han, PhD, Gallup, Inc."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

if (!require("pacman")) install.packages("pacman")
library ("pacman")
pacman::p_load(dplyr, ggplot2, Hmisc, gplots, car, tidyr, knitr, RCurl)

# download scripts and data
dlScripts <- function (scriptNames) {
  fileHolder <- getURL(paste(githubRepo, scriptNames, sep = "/"), ssl.verifypeer = FALSE)
  fileConn<-file(scriptNames)
  writeLines(fileHolder, fileConn)
  close(fileConn)
}
githubRepo <- "https://raw.githubusercontent.com/GallupGovt/ngs2/master/cycle4/Boomtown/Analysis"
tests <- c("survey_tests_cycle_4_code.R")
data <- c("game_survey_data.csv")
lapply(c(tests,data), dlScripts)
game_survey_data <- read.csv(file="game_survey_data.csv")
source("survey_tests_cycle_4_code.R")
```
# Participant Demos

```{r demos, echo=FALSE}
initial_survey <- gs[!duplicated(gs[,c('playerid')]),] 
demos <- c("Age_Group", "Gender", "Education_Group", "Employment_Status", "Online_Research_Experience")
apply(initial_survey[demos], 2, table, useNA = "always")
```

# Hypothesis Test Results Summary
```{r table, echo=FALSE}
kable(test_summary)
```

# Players Composition
## Age
### Age by Competition Condition
```{r age_comp_aov, echo=FALSE}
age_comp_aov$barplot
age_comp_aov$boxplot
```

### Age by Time Uncertainty Condition
```{r age_time_t, echo=FALSE}
age_time_t$barplot
age_time_t$boxplot
```

### Age by Tolerance Condition
```{r age_tole_t, echo=FALSE}
age_tole_t$barplot
age_tole_t$boxplot
```

### Age by Support Condition
```{r age_supp_t, echo=FALSE}
age_supp_t$barplot
age_supp_t$boxplot
```

### Age by Organizational Structure Condition
```{r age_stru_t, echo=FALSE}
age_stru_t$barplot
age_stru_t$boxplot
```

### Age Group by Competition Condition
```{r age_comp_chisq, echo=FALSE}
age_comp_chisq$barplot
```

### Age Group by Time Uncertainty Condition
```{r age_time_chisq, echo=FALSE}
age_time_chisq$barplot
```

### Age Group by Tolerance Condition
```{r age_tole_chisq, echo=FALSE}
age_tole_chisq$barplot
```

### Age Group by Support Condition
```{r age_supp_chisq, echo=FALSE}
age_supp_chisq$barplot
```

### Age Group by Organizational Structure Condition
```{r age_stru_chisq, echo=FALSE}
age_stru_chisq$barplot
```

## Gender
### Gender by Competition Condition
```{r gen_comp_chisq, echo=FALSE}
gen_comp_chisq$barplot
```

### Gender by Time Uncertainty Condition
```{r gen_time_chisq, echo=FALSE}
gen_time_chisq$barplot
```

### Gender by Tolerance Condition
```{r gen_tole_chisq, echo=FALSE}
gen_tole_chisq$barplot
```

### Gender by Support Condition
```{r gen_supp_chisq, echo=FALSE}
gen_supp_chisq$barplot
```

### Gender by Organizational Structure Condition
```{r gen_stru_chisq, echo=FALSE}
gen_stru_chisq$barplot
```

## Education Group
### Education Group by Competition Condition
```{r edu_comp_chisq, echo=FALSE}
edu_comp_chisq$barplot
```

### Education Group by Time Uncertainty Condition
```{r edu_time_chisq, echo=FALSE}
edu_time_chisq$barplot
```

### Education Group by Tolerance Condition
```{r edu_tole_chisq, echo=FALSE}
edu_tole_chisq$barplot
```

### Education Group by Support Condition
```{r edu_supp_chisq, echo=FALSE}
edu_supp_chisq$barplot
```

### Education Group by Organizational Structure Condition
```{r edu_stru_chisq, echo=FALSE}
edu_stru_chisq$barplot
```

## Employment Status
### Employment Status by Competition Condition
```{r emp_comp_chisq, echo=FALSE}
emp_comp_chisq$barplot
```

### Employment Status by Time Uncertainty Condition
```{r emp_time_prop, echo=FALSE}
emp_time_prop$barplot
```

### Employment Status by Tolerance Condition
```{r emp_tole_prop, echo=FALSE}
emp_tole_prop$barplot
```

### Employment Status by Support Condition
```{r emp_supp_prop, echo=FALSE}
emp_supp_prop$barplot
```

### Employment Status by Organizational Structure Condition
```{r emp_stru_prop, echo=FALSE}
emp_stru_chisq$barplot
```

## Online Research Experiment Experience
### Online Research Experiment Experience by Competition Condition
```{r ore_comp_chisq, echo=FALSE}
ore_comp_chisq$barplot
```

### Online Research Experiment Experience by Time Uncertainty Condition
```{r ore_time_prop, echo=FALSE}
ore_time_prop$barplot
```

### Online Research Experiment Experience by Tolerance Condition
```{r ore_tole_prop, echo=FALSE}
ore_tole_prop$barplot
```

### Online Research Experiment Experience by Support Condition
```{r ore_supp_prop, echo=FALSE}
ore_supp_prop$barplot
```

### Online Research Experiment Experience by Organizational Structure Condition
```{r ore_stru_chisq, echo=FALSE}
ore_stru_chisq$barplot
```

## Tolerance of Ambiguity (TA) by Tolerance Condition
```{r TA_tole_t, echo=FALSE}
TA_tole_t$barplot
TA_tole_t$boxplot
```

# Post-Game Survey
## Perceived Opponent Strength by Competition Condition
```{r POS_comp_aov, echo=FALSE}
POS_comp_aov$barplot
POS_comp_aov$boxplot
```

## Perceived Competition by Competition Condition
```{r PC_comp_aov, echo=FALSE}
PC_comp_aov$barplot
PC_comp_aov$boxplot
```

## Time Pressure by Round Type
```{r TP_round_pt, echo=FALSE}
TP_round_pt$barplot
TP_round_pt$boxplot
```

## Need of Fast Decision by Round Type
```{r FD_round_pt, echo=FALSE}
FD_round_pt$barplot
FD_round_pt$boxplot
```

## Amount of Information Processed by Voting Choices
```{r IP_tool_pt, echo=FALSE}
IP_tool_pt$barplot
IP_tool_pt$boxplot
```

## Certainty about Number of Rounds by Time Uncertainty Condition
```{r RC_time_t, echo=FALSE}
RC_time_t$barplot
RC_time_t$boxplot
```
