---
title: "NGS2-WITNESS - Cycle 4 Results: Hypothesis 2"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

### Hypothesis 2. Innovative Prospect Value and Individual Motivation to Innovate (T1) 

- Null: Prospect value will have no effect on Individual Motivation to Innovate (T1).

```{r}
cat(readLines("bayesGlmer_h2.1_h2.0_summary.txt"), sep = '\n')
```
- Prediction 1: Prospect value, per Cumulative Prospect Theory, will determine Individual Motivation to Innovate (T1).
- Prediction 2: Prospect value, per Expected Utility Theory, will determine Individual Motivation to Innovate (T1).
- Prediction 3: Prospect value, per Probability Theory, will determine Individual Motivation to Innovate (T1).
- Prediction 4: Prospect value, per a combination of CPT + Summative Expectancy Theory, will determine Individual Motivation to Innovate (T1).

```{r, fig.hold='hold', fig.hold='hold', out.width = "50%"}
source("functions.R")
Bf_plotter("BFs2.csv")
```

End Time: `r format(Sys.time(), '%d %B, %Y')`

<br />
<br />
<br />
