---
title: "Group Innovation under Competition and Uncertanity - Cycle 3 Results"
author: "Pablo Diego-Rosell, PhD  - Gallup"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list = ls(all = TRUE))
dd <- getwd()
od <- getwd()
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, strip.white=TRUE, tidy=TRUE)
# load libraries
if (!require("pacman")) install.packages("pacman", repos='http://cran.us.r-project.org')
library ("pacman")
pacman::p_load(rstan, rstanarm, ggplot2, Hmisc, httr, bridgesampling, DT, dplyr, bayesplot, knitr, lme4, RCurl, formatR, caret, pROC, formatR, foreach, doParallel, forcats, tidyr, car)
```
### Hypothesis 1. Intergroup Competition and Individual Motivation to Innovate (T1)

- Null: Intergroup competition has no effect on individual motivation to innovate (T1).

```{r h1null}
load (file ="bayesGlmer_h1_h1.1")
fittedGlmer
```
- Prediction 1: Intergroup competition increases Individual Motivation to Innovate (T1).

```{r }
load (file ="bayesGlmer_h1_h1.1")
fittedGlmer
```
- Prediction 2: Individual Motivation to Innovate (T1) is u-shaped on intergroup competition.
```{r }
load (file ="bayesGlmer_h1_h1.2")
fittedGlmer
```
- Prediction 3: Low intergroup competition decreases Individual Motivation to Innovate (T1).

```{r }
load (file ="bayesGlmer_h1_h1.3")
fittedGlmer
```

```{r h1BFs}
BFs1 <-read.csv(paste(od, "BFs1.csv", sep = '/'))                      
BFs1
```
